a and generators

### 2022-05-05 documentos/generators.tex
It only compiles every 3 tries... good luck.
Comentarios hechos

labels $\mcG_\alpha$ of the generators.

@@

>>>>

labels $\mcG_\alpha$ of the generators. \cpnote{Nadie ha revisado el nuevo caption y la nueva figura con cuidado}

@@

\janote{Acá dejo mi propuesta para la caption:}
\janote{A profound connection exists between the rows or columns of matrix $a$ 
(in turn, $A$) [refer to \eref{eq:lambda:is:A:tau}] that diagonalizes 
Choi's matrix of a PCE map and PCE generators $\mcG_\valpha$.
For instance, if one takes the columns of $a$ and replace all -1's with 0's one
is left with the sets of $\{\tau_\valpha\}$ of all single-qubit PCE generators.
The converse procedure is also valid, one goes from the PCE generators 
to the matrix $a$.}
